### 2018-02-13 manuscript/03_results.Rmd
Results: Revise CLM comparison
On closer examination...

A key application of this study was to provide data-driven parameter estimates for Earth System Models.
To this end, we compared our mean parameter estimates with corresponding default parameters in CLM 4.5 [@clm45_note] (Fig.\ 2).
Our mean estimates of SLA agreed with CLM's defaults [@clm45_note, Table 8.1] only for tropical broadleaved evergreen trees, and for all other PFTs, our estimates are significantly lower.
For $N_{mass}$, our estimates agreed reasonably well with CLM for evergreen temperate trees, needleleaved trees, and C3 arctic grasses, and were substantially different for all other PFTs.
Our $N_{mass}$ estimates also varied much more across PFTs than CLM's parameters.
For $N_{area}$, our estimates were significantly higher than CLM's for all PFTs, likely due to CLM's overestimates of SLA.
Our mean estimates of $V_{c,max_area}$ (among those that were reasonably constrained by data) were lower than those of CLM for all PFTs except needleleaf evergreen trees and grasses, for which our estimates overlapped CLM's parameters.
@kattge_2009_vcmax also found that $V_{c,max,area}$ was overestimated by Earth System models,
but their estimates of $V_{c,max,area}$ and $N_{area}$ are generally slightly higher than ours.

>>>>

A key application of this study was to provide data-driven parameter estimates for Earth System Models.
To this end, we compared our mean parameter estimates with corresponding default parameters in CLM 4.5 [@clm45_note] (Fig.\ 2).
Our mean estimates of SLA agreed with CLM's defaults [@clm45_note, Table 8.1] only for tropical broadleaved evergreen trees, and for all other PFTs, our estimates are significantly lower.
For $N_{mass}$, our estimates agreed reasonably well with CLM for evergreen temperate trees, needleleaved trees, and C3 arctic grasses, and were substantially different for all other PFTs.
Our $N_{mass}$ estimates also varied much more across PFTs than CLM's parameters.
For $N_{area}$, our estimates were significantly higher than CLM's for all PFTs, likely due to CLM's overestimates of SLA.
Our estimates of $V_{c,max_mass}$ were lower across all PFTs, with particularly large differences for tropical and temeprate broadleaf deciduous trees and evergreen shrubs, and temperate C3 grasses.
Our estimates of $V_{c,max,area}$ showed better agreement, though our values were still significantly lower for many PFTs.
Like us, @kattge_2009_vcmax also found that $V_{c,max,area}$ was overestimated by Earth System models,
but their estimates of $V_{c,max,area}$ and $N_{area}$ are generally slightly higher than ours.
